Structured Versus Decorated Cospans

### 2021-06-25 cospans_new.tex
Changed statement of Lemma 5.1

\begin{lem}
{\chris For $(F,\phi,\phi_0)\colon(\A,+)\to(\Cat,\times)$ a lax monoidal pseudofunctor, t}he double category $F\lCsp$ \textcolor{blue}{Kenny: of \cref{thm:decorated_cospans_1}}  is fibrant.
\end{lem}

>>>>

\begin{lem}
Given a category $\A$ with finite colimits and a lax monoidal pseudofunctor $(F,\phi,\phi_0) \maps (\A,+)\to(\Cat,\times)$, the double category $F\lCsp$ is fibrant.
\end{lem}
